Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Correcting some typos

When the offer phase is completed the seller has a set of all bids $B = {<b_i,p_i>}$. From this set they chose that subset of them which maximizes profit and is satisfiable. In essence satisfiability means that the same good cannot be sold more than once. Profit maximization computes for each satisfiable allocation $L \subset B$ the total value $v(L) = \sum \{p_i : <b_i,p_i> \subset L\}$ and chooses the maximum.\footnote{As explained in the first section there may be other objectives beside or instead of profit maximization in the auction but in commercial auctions the auctioneer's revenue is the main goal. So we will not provide further details for these expansions.}

@@

\cite{Nis00} calls this smallest possible bid of AND-connected items an ``atomic bid'' and also adds that if someone is willing to pay a price $p$ for a set $S$ of items they must also be willing to pay at least $p$ for any set $T$ with $S \subseteq T$. To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for. Such bids can look like the fooling example: $\{<\{a\},1>,<\{b\},2>,<\{a,b\},4>\}$

@@

During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.

>>>>

When the offer phase is completed the seller has a set of all bids $B = {<b_i,p_i>}$. From this set they choose that subset of them which maximizes profit and is satisfiable. In essence satisfiability means that the same good cannot be sold more than once. Profit maximization computes for each satisfiable allocation $L \subset B$ the total value $v(L) = \sum \{p_i : <b_i,p_i> \subset L\}$ and chooses the maximum.\footnote{As explained in the first section there may be other objectives beside or instead of profit maximization in the auction but in commercial auctions the auctioneer's revenue is the main goal. So we will not provide further details for these expansions.}

@@

\cite{Nis00} calls this smallest possible bid of AND-connected items an ``atomic bid'' and also adds that if someone is willing to pay a price $p$ for a set $S$ of items they must also be willing to pay at least $p$ for any set $T$ with $S \subseteq T$. To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundles he or she wants to bid for. Such bids can look like the fooling example: $\{<\{a\},1>,<\{b\},2>,<\{a,b\},4>\}$

@@

During the previous section some small examples were already given but the following ones will go a bit deeper into real world applications.

### 2014-06-29 review-log.tex
Rephrased and extended the explanation of different fair division strategies
Use of cannot and another instead of can not and an other
Correcting some typos

\section{Language \& Style}
\subsection{However sometimes either the wording is confusing or I do not get the message right. E.g. ``Another fairness criteria could be that the minimum utility is maximized.'' (1)}
\subsection{Another point is that it is more common to use cannot instead of `can not' and another instead of `an other'. (1)}
\subsection{Im Großen und Ganzen in Ordnung. Ein Zeitfehler in Kapitel 3, letzter Absatz: ``From this set they chose that'', hier gehört choose(Gegenwart) (2)}
\subsection{In section 4 Bidding Representations \& Languages the article says ``To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for.'' The word bundle is missing the -s ending for plural. (3)}
\subsection{Use of correct/better brackets in section 3 instead of less-than and greater-than signs. (3)}
\subsection{On page six the paper says ``During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.'' I think there is a typo and it should say real world applications. (3)}

>>>>

\section{Language \& Style}
\subsection{However sometimes either the wording is confusing or I do not get the message right. E.g. ``Another fairness criteria could be that the minimum utility is maximized.'' (1)}
Rephrased and extended.
\subsection{Another point is that it is more common to use cannot instead of `can not' and another instead of `an other'. (1)}
Searched and Replaced.
\subsection{Im Großen und Ganzen in Ordnung. Ein Zeitfehler in Kapitel 3, letzter Absatz: ``From this set they chose that'', hier gehört choose(Gegenwart) (2)}
Corrected typo.
\subsection{In section 4 Bidding Representations \& Languages the article says ``To be equivalent to the naive form these atomic bid must also be OR-conjunctional so that a bidder can submit several bundle he or she wants to bid for.'' The word bundle is missing the -s ending for plural. (3)}
Corrected typo.
\subsection{Use of correct/better brackets in section 3 instead of less-than and greater-than signs. (3)}
\subsection{On page six the paper says ``During the previous section some small examples were already given but the following ones will go a bit deeper into real work applications.'' I think there is a typo and it should say real world applications. (3)}
Corrected auto correction.
